\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-09-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Small changes

	\if1\blind
	{
		\title{\bf Forecast Reconciliation: A geometric view with new insights on bias correction.}
		\author{Anastasios Panagiotelis\thanks{
				The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3145, Australia.\\
			Email: Anastasios.Panagiotelis@monash.edu \\
			and \\
			Puwasala Gamakumara\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Puwasala.Gamakumara@monash.edu \\
			and \\
			George Athanasopoulos\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3145, Australia.\\
			Email: George.Athanasopoulos@monash.edu \\
			and \\
			Rob J Hyndman\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Rob.Hyndman@monash.edu \\}
		\maketitle
	} \fi

>>>>

	\if1\blind
	{
		\title{\bf Forecast Reconciliation: A geometric view with new insights on bias correction.}
		\author{Anastasios Panagiotelis\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3145, Australia.\\
			Email: Anastasios.Panagiotelis@monash.edu \\
			and \\
			Puwasala Gamakumara\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Puwasala.Gamakumara@monash.edu \\
			and \\
			George Athanasopoulos\thanks{Corresponding Author. The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3145, Australia.\\
			Email: George.Athanasopoulos@monash.edu \\
			and \\
			Rob J Hyndman\\
			Department of Econometrics and Business Statistics,\\
			Monash University,\\ VIC 3800, Australia.\\
			Email: Rob.Hyndman@monash.edu \\}
		\maketitle
	} \fi
